Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-06-22 doc/main_jfm.tex
updates

The results of the reduced area are shown in Figure~\ref{figure4} where we compare the change of area over the time with a set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$. The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ is the vesicle area and $L$ is the arc length of the vesicle with respect to the midplane. Since the starting configuration is close to a circular shape, the reduced are decreases from a value very close to $1$. It is clear that a slower shear rate generates a higher reduced area and has faster convergence. The small oscillations in all results are due to the granular setup of the bilayer which tends to having a slightly non-smooth curve in simulations.

\begin{figure}
\begin{center}
\includegraphics[width=0.4\textwidth]{ArcLength.pdf}
\includegraphics[width=0.4\textwidth]{ReducedArea.pdf}
\end{center} 
  \caption{(a) Total arc lengths of the outer leaflets over time in different shear rates; (b)Reduced area transitions over time. 
A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
A slower shear rate generates a faster convergence in the reduced area. 
  }
    \label{figure4}
\end{figure}

>>>>

In order to extract more physical properties of the proposed model, we track the total length of the bilayer structure and the reduced area over the time.
These results are shown in Figure~\ref{figure4} where we compare output the results from a set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$. 
The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ is the vesicle area and $L$ is the arc length of the vesicle with respect to the midplane. Since the starting configuration is close to a circular shape, the reduced are decreases from a value very close to $1$. It is clear that a slower shear rate generates a higher reduced area and has faster convergence. The small oscillations in all results are due to the granular setup of the bilayer which tends to having a slightly non-smooth curve in simulations.

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{ArcLength.pdf}
\includegraphics[width=0.45\textwidth]{ReducedArea.pdf}
\end{center} 
  \caption{(a) Total arc lengths of the outer leaflets over time in different shear rates; (b)Reduced area transitions over time. 
A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
A slower shear rate generates a faster convergence in the reduced area. 
  }
    \label{figure4}
\end{figure}
